Generating Simulated Data

### 2021-03-30 docs/SimData.Rmd
try different start values vbgf

  svvbgf <- svlenage %>%
    dplyr::group_by(species, era) %>%
    group_map(~nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .)))

@@

>>>>

  saveRDS(svlenage, file.path(d.name, paste0(scenario.name, "_",
                                                       s, "agelensamp.rds")))
  #plot len-age data and start values, some are bad
  svlenage_pl <- svlenage %>%
    group_by(species, era) %>%
    group_map(~vbStarts(length~avgage,data=cur_group(),plot=TRUE))

@@

```{r vbfits-scratch, eval=FALSE}

  capelinvbgf <- svlenage %>%
    filter(species == "Capelin") %>%
    group_by(era) %>%
    group_map(try(~nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .))))

  capelinall <- svlenage %>% filter(species == "Capelin")
  plot(length~avgage,data=capelinall,pch=19,col=rgb(0,0,0,1/5))
  curve(vb1(x,Linf=coef(capelinvbgf[[1]])),from=0,to=5,col="red",lwd=2,add=TRUE)
  curve(vb1(x,Linf=coef(capelinvbgf[[2]])),from=0,to=5,col="blue",lwd=2,add=TRUE)
  curve(vb1(x,Linf=coef(capelinvbgf[[3]])),from=0,to=5,col="green",lwd=2,add=TRUE)

  # herringvbgf <- svlenage %>%
  #   filter(species == "Norweigan_ssh", era==1) %>%
  #   group_map(try(~nls(length~vb1(avgage, Linf, K, t0), data = .,
  #                 start = vbStarts(length~avgage,data = .))))

#Error in nls(length ~ vb1(avgage, Linf, K, t0), data = ., start = vbStarts(length ~  : 
  #singular gradient with group_map, era 2 and 3
  codvbgf <- svlenage %>%
    filter(species == "North_atl_cod") 
    #group_by(era) %>%
    codfit <- nls(length~vb1(avgage, Linf, K, t0), data = codvbgf,
                  start = vbStarts(length~avgage,data = codvbgf))

    plot(length~avgage,data=codvbgf,pch=19,col=rgb(0,0,0,1/5))
    curve(vb1(x,Linf=coef(codfit)),from=0,to=20,col="red",lwd=2,add=TRUE)
#  era==1   Nonlinear regression model
#   model: length ~ vb1(avgage, Linf, K, t0)
#    data: codvbgf
#     Linf        K       t0 
# 104.7120   0.4260   0.2176 
#  residual sum-of-squares: 4109723
# 
# Number of iterations to convergence: 7 
# Achieved convergence tolerance: 2.169e-06

#  all years Nonlinear regression model
#   model: length ~ vb1(avgage, Linf, K, t0)
#    data: codvbgf
#     Linf        K       t0 
# 112.4694   0.3912   0.2097 
#  residual sum-of-squares: 7354906
# 
# Number of iterations to convergence: 11 
# Achieved convergence tolerance: 9.964e-06

  hadvbgf <- svlenage %>%
    filter(species == "Haddock") 
    #group_by(era) %>%
  hadfit <- nls(length~vb1(avgage, Linf, K, t0), data = hadvbgf,
                  start = vbStarts(length~avgage,data = hadvbgf))

  plot(length~avgage,data=hadvbgf,pch=19,col=rgb(0,0,0,1/5))
  curve(vb1(x,Linf=coef(hadfit)),from=0,to=20,col="red",lwd=2,add=TRUE)

# all years
#     Nonlinear regression model
#   model: length ~ vb1(avgage, Linf, K, t0)
#    data: hadvbgf
#    Linf       K      t0 
# 77.0277  0.3601 -0.3546 
#  residual sum-of-squares: 15637500
# 
# Number of iterations to convergence: 11 
# Achieved convergence tolerance: 4.187e-06

  redvbgf <- svlenage %>%
    filter(species == "Redfish") 
    #group_by(era) %>%

  redfit <- nls(length~vb1(avgage, Linf, K, t0), data = redvbgf,
                  start = vbStarts(length~avgage,data = redvbgf))

  plot(length~avgage,data=redvbgf,pch=19,col=rgb(0,0,0,1/5))
  curve(vb1(x,Linf=coef(redfit)),from=0,to=40,col="red",lwd=2,add=TRUE)

#all years
# Nonlinear regression model
#   model: length ~ vb1(avgage, Linf, K, t0)
#    data: redvbgf
#    Linf       K      t0 
# 40.8016  0.1165 -1.6688 
#  residual sum-of-squares: 3197990
# 
# Number of iterations to convergence: 13 
# Achieved convergence tolerance: 8.316e-06

    saithe1 <- svlenage %>%
      filter(species=="Saithe",
             era==1)

    saithe1fit <- nls(length~vb1(avgage, Linf, K, t0), data = saithe1,
                  start = vbStarts(length~avgage,data = saithe1))

    plot(length~avgage,data=saithe1,pch=19,col=rgb(0,0,0,1/5))
    curve(vb1(x,Linf=coef(saithe1fit)),from=0,to=20,col="red",lwd=2,add=TRUE)
#Nonlinear regression model
#   model: length ~ vb1(avgage, Linf, K, t0)
#    data: saithe1
#      Linf         K        t0 
# 388.18797   0.01975  -3.94798 
#  residual sum-of-squares: 5691213
# 
# Number of iterations to convergence: 5 
# Achieved convergence tolerance: 5.511e-06

### full time series fits with different start points

 svvbgf <- svlenage %>%   
    dplyr::group_by(species) %>%
    group_map(~try(nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .))))

 spk <- svlenage %>%
   group_by(species) %>%
   group_keys()

vballout <- data.frame() 
for(i in 1:length(svvbgf)) {
  if(is.list(svvbgf[[i]])) {
    sp <- cbind(as.data.frame(spk)[i,], t(coef(svvbgf[[i]])))
    vballout <- rbind(vballout, sp)
  }
}

svvbgf.1 <- svlenage %>%   
    dplyr::group_by(species) %>%
    group_map(~try(nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .,methLinf="oldAge"))))

vballout.1 <- data.frame() 
for(i in 1:length(svvbgf.1)) {
  if(is.list(svvbgf.1[[i]])) {
    sp <- cbind(as.data.frame(spk)[i,], t(coef(svvbgf.1[[i]])))
    vballout.1 <- rbind(vballout.1, sp)
  }
}

svvbgf.2 <- svlenage %>%   
    dplyr::group_by(species) %>%
    group_map(~try(nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .,methLinf="longFish"))))

vballout.2 <- data.frame() 
for(i in 1:length(svvbgf.2)) {
  if(is.list(svvbgf.2[[i]])) {
    sp <- cbind(as.data.frame(spk)[i,], t(coef(svvbgf.2[[i]])))
    vballout.2 <- rbind(vballout.2, sp)
  }
}

################## by era

 gk <- svlenage %>%
   group_by(species, era) %>%
   group_keys()

 svvbgf3 <- svlenage %>%   
    dplyr::group_by(species, era) %>%
    group_map(~try(nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .))))

vbout <- data.frame() 
for(i in 1:length(svvbgf3)) {
  if(is.list(svvbgf3[[i]])) {
    spe <- cbind(as.data.frame(gk)[i,], t(coef(svvbgf3[[i]])))
    vbout <- rbind(vbout, spe)
  }
}

# try different start points to see if we can get more species fit
 svvbgf3.1 <- svlenage %>%   
    dplyr::group_by(species, era) %>%
    group_map(~try(nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .,methLinf="oldAge"))))

vbout.1 <- data.frame() 
for(i in 1:length(svvbgf3.1)) {
  if(is.list(svvbgf3.1[[i]])) {
    spe <- cbind(as.data.frame(gk)[i,], t(coef(svvbgf3.1[[i]])))
    vbout.1 <- rbind(vbout.1, spe)
  }
}

# try different start points to see if we can get more species fit
# this one goes to 11!
svvbgf3.2 <- svlenage %>%   
    dplyr::group_by(species, era) %>%
    group_map(~try(nls(length~vb1(avgage, Linf, K, t0), data = .,
                  start = vbStarts(length~avgage,data = .,methLinf="longFish"))))

vbout.2 <- data.frame() 
for(i in 1:length(svvbgf3.2)) {
  if(is.list(svvbgf3.2[[i]])) {
    spe <- cbind(as.data.frame(gk)[i,], t(coef(svvbgf3.2[[i]])))
    vbout.2 <- rbind(vbout.2, spe)
  }
}
